---
title: "poweranalysis_vanharreveldetal2014"
author: "Daniel Toribio Flórez"
date: "21/1/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages:

```{r, include=FALSE}
library(haven)
library(psych)
library(pwr)
```

Read data set:

```{r}
df_vanharreveldetal <- read_sav(file = "./data_vanharreveldetal2014.sav")
```

# Effect sizes of interest:

Estimate effect size of interest and lower bound of 80% CIs to use as reference effect size for a priori safeguard power analyses (Perugini et al. 2014).

### Correlation Subjective Ambivalence (Priester & Petty, 1996) and Conspiracy Beliefs:

```{r}
eff1 <- cor.test(df_vanharreveldetal$Pettyscale, 
         df_vanharreveldetal$conspiracyscale,
         conf.level = .80)
eff1
```

Estimate sample size to detect r = `eff1$conf.int[1]`:
```{r}
pwr.r.test(n = NULL,
           r = eff1$conf.int[1],
           sig.level = .05,
           power = .95,
           alternative = "two.sided")
```
### Difference between Ambivalence vs. Univalence condition:

```{r}
t.test(df_vanharreveldetal$conspiracyscale ~ df_vanharreveldetal$condition)
eff2 <- cohen.d(df_vanharreveldetal$conspiracyscale, df_vanharreveldetal$condition,
        alpha = 0.2)
eff2
```
Estimate sample size to detect r = `eff2$cohen.d[1]`:

```{r}
pwr.t.test(n = NULL, 
           d = eff2$cohen.d[1],
           sig.level = .05,
           power = .95,
           type = "two.sample",
           alternative = "two.sided"
           )
```

