---
title: "study1_replication_vanharreveld"
author: "Daniel Toribio Flórez"
date: "24/1/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages:

```{r, include=FALSE}
library(tidyverse)
library(psych)
library(visdat)
library(DataExplorer)
library(parameters)
```

Read data set:

```{r}
df_study1 <- read_csv2(file = "./study1_replication_vanharreveld.csv") %>% 
  type_convert(guess_integer = FALSE)
```

Sanity check: Detect multiple responses from the same Prolific IDs.
```{r}
df_study1  %>% 
  group_by(PROLIFIC_PID) %>% 
  count() %>% 
  arrange(desc(n))
```

Anonymize data, remove unnecessary columns and create ParticipantID:
```{r}
df_study1 <- df_study1 %>%
  mutate(ParticipantID = seq.int(nrow(.))) %>%
  select(ParticipantID, everything()) %>% 
  select(-c("IPAddress", "Finished", "RecordedDate", "ResponseId", "RecipientLastName", "Status",
         "RecipientFirstName", "RecipientEmail", "ExternalReference", "LocationLatitude",
         "LocationLongitude","DistributionChannel","UserLanguage","PROLIFIC_PID"))
```

### Exclusion Criteria:
Number of participants before exclusion criteria:
```{r}
before_exclusions <- nrow(df_study1)
```

Exclude people that did not accept Informed Consent:
```{r}
df_study1 <- df_study1 %>%
  filter(informedconsent == 1)

no_consent <- before_exclusions - nrow(df_study1)
```


Attention checks:
```{r}
df_study1 <- df_study1 %>% 
  filter(AttCheck1 == 1 | AttCheck2 == 1) #That answered correctly at least one Attention check.

fail_attchecks <- before_exclusions - no_consent - nrow(df_study1)
```

# Variable Type/Recoding:

```{r}
df_study1 <- df_study1 %>% 
  mutate(condition = as.factor(condition),
         condition = fct_relevel(condition, "Univalence")) 
```


## Descriptive exploration of dataset:

### Missing observations

```{r}
df_study1 %>% vis_miss()
```

```{r}
df_study1 %>% plot_missing()
```

## Answer distributions:

```{r evaluate = FALSE}
df_study1 %>%
  select(starts_with("SA_"), starts_with("NegEmo"), starts_with("conspiracy"), Age, Education) %>% 
    plot_histogram()
```

## Compute Variables:

### Subjective Ambivalence:
Internal consistency
```{r}
alpha(as.matrix(df_study1[,c("SA_1_1","SA_2_1","SA_3_1")]),na.rm = TRUE)
```
Compute average score:
```{r}
df_study1 <- df_study1 %>% 
  mutate(SA = rowMeans(df_study1[,c("SA_1_1","SA_2_1","SA_3_1")],na.rm = TRUE))
```

### Negative Emotions:
Internal consistency
```{r}
alpha(as.matrix(df_study1[,c("NegEmo_1", "NegEmo_2", "NegEmo_3", "NegEmo_4", "NegEmo_5")]),na.rm = TRUE)
```

Compute average score:
```{r}
df_study1 <- df_study1 %>% 
  mutate(NegEmo = rowMeans(df_study1[,c("NegEmo_1", "NegEmo_2", "NegEmo_3", "NegEmo_4", "NegEmo_5")],na.rm = TRUE))
```

### Conspiracy Beliefs:
Internal consistency
```{r}
#Splithalf reliability based on Spearman-Brown prophecy formula: ((2 * r) / (1 + r))
r <- cor(df_study1[,c("conspiracy_1_1","conspiracy_2_1")],use = "na.or.complete")
sb_conspiracy <- (2*r[2,1])/(1+r[2,1])
```

Compute average score:
```{r}
df_study1 <- df_study1 %>% 
  mutate(conspiracy_beliefs = rowMeans(df_study1[,c("conspiracy_1_1","conspiracy_2_1")],na.rm = TRUE))
```


# Analysis

## Manipulation Check:

```{r}
t.test(df_study1$SA ~ df_study1$condition)
```

## Main Analyses

### Does the level of conspiracy beliefs differ across experimental conditions?

```{r}
mod1 <- lm(conspiracy_beliefs ~ condition,
           df_study1)
model_parameters(mod1)
```

**Expected results:**

H1a. Participants in the Ambivalence condition will report higher conspiracy beliefs when interpreting an ambiguous scenario than those in the Univalent condition.

-> Significant positive weight of `condition` term (i.e., significant difference between means).

Calculate Cohen's d:
```{r}
cohen.d(df_study1$conspiracy_beliefs, df_study1$condition)
```

### Does participants' level of reported Subjective Ambivalence predict conspiracy beliefs?

```{r}
cor.test(df_study1$SA, df_study1$conspiracy_beliefs)
```

**Expected results:**

H1b. Participants´ self-reported Subjective Ambivalence will positively predict conspiracy beliefs when interpreting ambiguous scenarios.

-> Significant positive correlation between `SA` and `conspiracy_beliefs`.

### Do negative emotions mediate the effect of ambivalence on conspiracy beliefs?

PROCESS macro for mediation analysis do not accept factor variables. Create a numeric version of variable `condition`:
```{r}
df_study1 <- df_study1 %>% 
  mutate(condition_num = as.numeric(recode(condition,
                                           "Ambivalence" = 1,
                                           "Univalence" = 0)))
```

Fit hypothesized mediation model:
```{r}
mod_mediation <- process(df_study1,
        y = "conspiracy_beliefs",
        x = "condition_num",
        m = "NegEmo",
        seed = 1234,
        model = 4,
        iterate = 500)
```

**Expected results:**

H2. Negative emotions will mediate the effect of ambivalence on conspiracy beliefs. 

-> Significant indirect effect of `NegEmo`.
-> Significant positive effect of `condition_num` on `NegEmo`, and significant positive effect of `NegEmo` on `conspiracy_beliefs`.

